---
title: "Collaborative Assessments"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r imports, message=FALSE, warning=FALSE}
library(tidyverse)
library(bsplus)
library(htmltools)
```

This course will use a form of collaborative assessment as a means of assessing your work. Collaborative assessment is a system of assessment that encourages students to focus more on growth and improvement towards certain learning objectives rather than achieving a certain quantitative score. Since this course convenes students with different types of expertise, collaborative assessment also honors the diversity of skills and modes of engagement that students are bringing to and improving throughout the course. As an instructor of such a course, when it comes to assignments, my role is more about providing feedback and less about measuring the quality of your work against certain pre-determined standards. In this course, you will formally reflect on how much effort you put into each assignment and what you think you achieved; I will offer my own assessments of how much effort I see reflected in your work and what I think you achieved. I will also offer suggestions for improvements to your work going forward. Together, we will use these assessments to determine your final grade.

## How will this work, more specifically?

To earn an A in this course, you must complete **all assignments** on the syllabus on time or by the date/time of an agreed upon extension. Any incomplete or late assignments will be docked a certain number of points from your final grade (the point amount will be specified in the course schedule). Given the clinic-based nature of this course, there are certain things you will need to do just to keep the project moving forward. These assignments will be graded for completion; as long as you complete the assignment on time, you will earn full credit for the assignment. 

Other assignments will require you to engage in critical thinking, to define and situate technical problems, to devise creative solutions, or to reflect on your experiences. When submitting these assignments, you will provide an initial self-assessment of your work by filling out a form that will be attached to the assignment. Each form will be tailored towards the assignment, but in general, you will be asked to document the degree of effort you put into the assignment, your technical execution of the assignment, and the depth of reflection you engaged throughout the assignment, each on a scale of 1-10. I will then offer my own feedback on your assignments. After this, you will have an opportunity to revise your self-assessment based on my feedback. Please note that I reserve the right to adjust self-assessment scores if I find them considerably out of sync with my own assessments of your work. 

Self-assessment scores will be averaged mid-semester to help you understand where you stand in the course. They will be averaged again at the end of the semester to determine your final grade. After this, the completion points associated with assignments you did not complete will be subtracted from the averaged grade, along with points associated with absences beyond the first three.

## What time do I need to submit assignments?

Assignments are due **before class** (10:50AM EST) on the designated due date. If you take the 24-hour grace period for individual written assignments (note that this is not an option for reading assignments adn group assignments), the assignment is due before (10:50AM EST) on the day following the designated due date. Any granted extensions are similarly due before 10:50AM EST on the date the deadline is extended to.


## What are reading assignments?

Most weeks a selection of course readings will be posted as a single assignment on Perusall - a system for students to collaboratively annotate course readings. You will be expected to post 3 quality annotations per assignment to Perusall. A quality annotation is one in which you synthesize concepts, ask thought-provoking questions, or connect ideas to external issues. I have found that students get the most out of Perusall when they respond to each other’s annotations. Each incomplete reading assignment will result in 2 points docked from the final grade. Annotations must be completed **before class** to receive credit.

## How does attendance factor in to the final grade?

See our [course attendance policy](index.html#Attendance). Note that, after the first 3 unexcused absences, 5 points will be subtracted from your averaged final grade for each additional absence. Late arrivals (>10 minutes late) that haven't been approved by me ahead of time will be counted as absences. 

## Why are deadlines and the completion of assignments enforced so strongly in this course?

You have registered for a course that demands a great deal of accountability to different stakeholders. Deadlines in this course are not arbitrary. I've paced them very deliberately to ensure that you can complete a project for a real-world organization by the time that they need the outputs of that project. As a class, we are accountable to a real-world project sponsor; incomplete assignments could mean that our project sponsors cannot achieve their goals. We are also accountable to each other. Non-completion of assignments could hold up other groups that are supposed to build-off of foundational work. If the timely completion of assignments could pose a problem for you, I encourage you to speak with me as soon as possible.

## What can I expect regarding the flow of this course?

This course is designed to have a large group of students collaboratively scope and tackle a real-world project. I have done the best that I can to structure our course in ways that enable you to approach that project systematically and in accordance with certain tried-and-true project management frameworks. However, as with any real world project, I can't anticipate everything that will come up. Further, the scope of many assignments that will be completed later in the course is dependent on what we learn along the way. In enrolling in this course, you are choosing to engage in a learning environment that has a certain degree of uncertainty built-in. I see this as the primary pedagogical value of a course like this; you're learning how to approach and adapt to the messiness of real world environments. 

